Figure 1 - overview

### 2024-07-05 ms_figure_1_overview.Rmd
add TF construct sequences and link from figure 1
Co-authored-by: Charlotte Soneson <charlottesoneson@gmail.com>
Co-authored-by: Michael Stadler <stadler.michael@gmail.com>
Rearrange panels in Figure 1, highlight meiosis-specific TFs

ave_tpm <- data.frame(
    bait = allbaits, 
    bait_pulled = factor(
        ifelse(.capitalize(allexps) %in% nobait_150, 
               "Bait not pulled down (150 mM NaCl IP-MS)",
               "Bait pulled down (150 mM NaCl IP-MS)"),
        levels = c("Bait pulled down (150 mM NaCl IP-MS)",
                   "Bait not pulled down (150 mM NaCl IP-MS)")),
    tpm = rowMeans(assay(rnaseq, "abundance")[allbaits, 
                                              rnaseq$Group_name == "wt_WT_mRNA"])
)
gg_tpm <- ggplot(ave_tpm, aes(x = fct_reorder(bait, tpm, .desc = TRUE), y = tpm, 
                              color = bait_pulled)) + 
    geom_hline(yintercept = 0, linetype = "dashed", color = na_color) +
    geom_point(size = 1) + 
    theme_cowplot() + 
    theme(legend.position = "inside", legend.position.inside = c(0.15, 0.9)) +
    scale_color_manual(values = c("Bait pulled down (150 mM NaCl IP-MS)" = pt_color,
                                  "Bait not pulled down (150 mM NaCl IP-MS)" = na_color),
                       name = "") + 
    guides(color = guide_legend(nrow = 2, byrow = TRUE)) + 
    labs(x = "Transcription factors",
         y = "Transcription factor\ngene expression (TPM)")
(gg_tpm + theme(axis.text.x = element_blank(), 
                axis.ticks.x = element_blank()))
```

@@

For each sample, the unmapped reads were aligned against all tagged
transcription factor sequences. The resulting  alignment counts are summarized
in the `tagcnt` matrix of `r nrow(tagcnt)` rows by `r ncol(tagcnt)` columns.
The rows correspond to tagged transcription factor sequences, and the columns
to *S. pombe* strains in which a transcription factor has been tagged.
The values correspond to the number of read pairs from ChIP input samples of
each strain, that mapped unambigously to one of the expected tagged
transcription factor constructs.

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        gg_dbd, 
        gg_tpm + theme(axis.text.x = element_blank(), 
                       axis.ticks.x = element_blank()),
        nrow = 1,
        labels = c("A", "B"),
        align = "vh",
        axis = "b"
    ),
    fig1c,
    cowplot::plot_grid(
        gg_nbrint,
        gg_nbrpeaks_all_narrow_by_npeaks,
        nrow = 1, 
        labels = c("D", "E"),
        align = "vh", 
        axis = "b"
    ),
    nrow = 3,
    labels = c(NA, "C", NA),
    align = "v",
    axis = "b",
    rel_heights = c(50, 73, 50)
)
```

>>>>

ave_tpm <- data.frame(
    bait = allbaits, 
    bait_pulled = factor(
        ifelse(.capitalize(allexps) %in% nobait_150, 
               "Bait not pulled down (150 mM NaCl IP-MS)",
               "Bait pulled down (150 mM NaCl IP-MS)"),
        levels = c("Bait pulled down (150 mM NaCl IP-MS)",
                   "Bait not pulled down (150 mM NaCl IP-MS)")),
    tpm = rowMeans(assay(rnaseq, "abundance")[allbaits, 
                                              rnaseq$Group_name == "wt_WT_mRNA"])
)
gg_tpm <- ggplot(ave_tpm, aes(x = fct_reorder(bait, tpm, .desc = TRUE), y = tpm, 
                              color = bait_pulled)) + 
    geom_hline(yintercept = 0, linetype = "dashed", color = na_color) +
    geom_point(size = 1) + 
    theme_cowplot() + 
    theme(legend.position = "inside", legend.position.inside = c(0.15, 0.9)) +
    scale_color_manual(values = c("Bait pulled down (150 mM NaCl IP-MS)" = pt_color,
                                  "Bait not pulled down (150 mM NaCl IP-MS)" = na_color),
                       name = "") + 
    scale_x_discrete(breaks = c("mei4", "atf31", "atf21", "cuf2", "rsv1")) + 
    guides(color = guide_legend(nrow = 2, byrow = TRUE)) + 
    labs(x = "Transcription factors",
         y = "Transcription factor\ngene expression (TPM)")
(gg_tpm + theme(axis.text.x = element_blank(),
                axis.ticks.length.x = unit(2, "mm"),
                axis.ticks.x = element_line(color = main_colors[1],
                                            linewidth = 1.25)))
```

@@

For each sample, the unmapped reads were aligned against all tagged
transcription factor sequences (see file [`reference/TFome_pombe_strain_lib.fasta`](reference/TFome_pombe_strain_lib.fasta)). The resulting  alignment counts are summarized
in the `tagcnt` matrix of `r nrow(tagcnt)` rows by `r ncol(tagcnt)` columns.
The rows correspond to tagged transcription factor sequences, and the columns
to *S. pombe* strains in which a transcription factor has been tagged.
The values correspond to the number of read pairs from ChIP input samples of
each strain, that mapped unambigously to one of the expected tagged
transcription factor constructs.

@@

cowplot::plot_grid(
    fig1c,
    cowplot::plot_grid(
        gg_dbd, 
        gg_tpm + theme(axis.text.x = element_blank(),
                       axis.ticks.length.x = unit(2, "mm"),
                       axis.ticks.x = element_line(color = main_colors[1],
                                                   linewidth = 1.25)),
        nrow = 1,
        labels = c("B", "C"),
        align = "vh",
        axis = "b"
    ),
    cowplot::plot_grid(
        gg_nbrint,
        gg_nbrpeaks_all_narrow_by_npeaks,
        nrow = 1, 
        labels = c("D", "E"),
        align = "vh", 
        axis = "b"
    ),
    nrow = 3,
    labels = c("A", NA, NA),
    align = "v",
    axis = "b",
    rel_heights = c(73, 50, 50)
)
```
